### 2010-01-26 trunk/deliverables/D5_1_2/fast_d5_1_2.tex
deliverable ready for review
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@476 d8b0c59b-6544-0410-94d9-83a5658a058e

\subsection{Overall approach for WP5 and relation to other Work Packages and Deliverables} % (fold)
\label{sub:overall_approach_for_wp5}

The main objective of the Work Package 5, as specified in \cite{DoW}, includes the development of the FAST semantic catalogue, considered the back-end of the FAST platform, which will store and index any kind of resources such as screen-flows, screens, back-end Web services descriptions, locate appropriate gadgets, resources and Web services for users, storing and indexing user profiles, and resolve mediation problems between gadgets, back-end services and the different ontologies stored.

The deliverables stated in \cite{DoW} for this WP are:
\begin{description}
	\item[User manual of the FAST Catalogue] This is the user manual of the catalogue. Since the semantic catalogue will not provide a user graphical interface by itself: it relies on the GVS; this document will be oriented to developers, explaining technical aspects of the catalogue, its API and several examples to ease its use.
	\item[Prototype semantic catalogue for screen-flow gadgets and back-end services] This deliverable is a software prototype of the semantic catalogue for experimentation purposes.
\end{description}

The semantic catalogue relies strongly on the FAST ontology defined in \cite{moeller2009fast_ontology} since the ontology defines how every element within FAST will be internally stored by the catalogue, and takes into consideration specific requirements detailed in \cite{fast_requirements} where the functionalities of the complete FAST tool are defined.

% subsection overall_approach_for_wp5 (end)

\subsection{Changes from D5.2.1} % (fold)
\label{sub:changes}

@@

\begin{itemize}
	\item Section \ref{sec:installation_guide}. Installation Guide describes a set of steps to be followed in order to install and execute the FAST Catalogue. Also some configuration instructions are specified.
	\item Section \ref{sub:content_negotiation}. Content Negotiation states how the FAST Catalogue has adopted several of the content negotiation principles.
	\item Section \ref{sec:restful_catalogue_api}. RESTful Catalogue API has been intensively extended and modified in order to  reflect all the new functionality and how every request or response is constructed.
	\item Several appendixes have been added with the JSON structure of every building block the Catalogue can deal with.
\end{itemize}

% subsection changes (end)

@@

The format supported by the Catalogue API for all the request and responses is JSON\footnote{http://www.json.org/}. JSON is a lightweight data interchange format whose simplicity has resulted in widespread use among web developers, easy to read and write and able to using any programming language because its structures map directly to data structures used in most programming languages.

Every HTTP request and response is encoded using the MIME type \texttt{application/json} and the charset \texttt{UTF-8}.

\subsubsection{Example of a screen}
\begin{verbatim}
{
  "uri": null,
  "label": {"en-GB": "Screen - DERI"},
  "description": {"en-GB": "Returns people working in DERI"},
  "creationDate": "2009-02-07T09:59:52+0000",
  "creator": "http://www.ismaelrivera.es/",
    "domainContext": {
      "tags": [],
      "user": null
    },
  "homepage": "http://www.deri.ie/",
  "icon": "http://www.deri.ie/icon.jpg",
  "screenshot": "http://www.deri.ie/screenshot.jpg",
  "rights": "http://creativecommons.org/",
  "version": "1.0",
  "preconditions": [],
  "postconditions": ["?person rdf:type foaf:Person . 
                      ?person foaf:workplaceHomepage http://www.deri.ie/"]
}
\end{verbatim}

@@

In order to offers an adaptable solution to various languages and regions without major engineering changes, internationalisation is considered from an early stage in the catalogue development. Underlying representation technologies used to develop the catalogue (RDF and JSON) allow to implement this feature. This feature is implemented by the addition of a language tag to every 'string' desired. The specification of this language tag is composed by the language code and the country code, following the ISO 639\footnote{http://ftp.ics.uci.edu/pub/ietf/http/related/iso639.txt} for languages and the ISO 3166\footnote{http://userpage.chemie.fu-berlin.de/diverse/doc/ISO\_3166.html} for countries. The following example illustrates how to use it properly in both formats.

@@

By now it is allowed using internationalisation for the label and the description of a screen, but more attributes will be benefited by this feature.

@@

\subsubsection{CRUD operations for Screens} % (fold)

A screen is a resource which can be created, retrieved, modified or deleted since the catalogue provides CRUD support for screens. These features are provided following the REST philosophy, using the HTTP methods. Two concepts have to be defined: \emph{collection}, as a set of screens which access URI is http://catalogueURL/screens/ where catalogueURL is the specific URL where the catalogue server is installed, and \emph{member} of the collection, in other words, the screen itself, which access URI is http://catalogueURL/screens/<id> where the <id> has to be replaced by the identifier of a screen. The details of the operations and which HTTP verb has to be used can be found in the Table \ref{tab:crud_screens}.

\begin{table}[htb]
\caption{CRUD operations for Screens}
\label{tab:crud_screens}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{2.5cm}|p{3.5cm}|p{5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Resource} &
                         \textcolor{white}{HTTP method} &
                         \textcolor{white}{HTTP body} &
                         \textcolor{white}{Description}\\ \hline
Collection URI & GET & N/A & \textbf{List} the members of the collection.\\ \hline
Collection URI & PUT & N/A & Not used.\\ \hline
Collection URI & POST & JSON representation of the screen & \textbf{Create} a new entry in the collection where the URI is assigned automatically by the collection. The URI created is returned by this operation.\\ \hline
Collection URI & DELETE & N/A & Not used.\\ \hline
Member URI & GET & N/A & \textbf{Retrieve} the addressed member of the collection.\\ \hline
Member URI & PUT & JSON representation of the screen & \textbf{Update} the addressed member of the collection or create it with a defined URI.\\ \hline
Member URI & POST & N/A & Not used. \\ \hline
Member URI & DELETE & N/A & \textbf{Delete} the addressed member of the collection.\\ \hline
\end{tabular}
\end{center}
\end{table}

Here are shown various examples of request and responses using the catalogue server. To create a new screen, a POST request is send to the catalogue server, including the JSON representation of the screen as the body of the request:

\begin{verbatim}
{
  "uri": null,
  "label": {"en-GB": "Screen - DERI"},
  "description": {"en-GB": "Returns people working in DERI"},
  "creationDate": "2009-02-07T09:59:52+0000",
  "creator": "http://www.ismaelrivera.es/",
    "domainContext": {
      "tags": [],
      "user": null
    },
  "homepage": "http://www.deri.ie/",
  "icon": "http://www.deri.ie/icon.jpg",
  "screenshot": "http://www.deri.ie/screenshot.jpg",
  "rights": "http://creativecommons.org/",
  "version": "1.0",
  "preconditions": [],
  "postconditions": ["?person rdf:type foaf:Person . 
                      ?person foaf:workplaceHomepage http://www.deri.ie/"]
}
\end{verbatim}

The URI will be not taken into account since the catalogue will generate a unique URI for each resource created. So, the response for this operation is:

\begin{verbatim}
{
  "creationDate": "2009-02-07T09:59:52+0000",
  "creator": "http://www.ismaelrivera.es/",
  "description": {"en-GB": "Show information about a person working in DERI"},
  "domainContext": {
    "tags": [],
    "user": "null"
  },
  "homepage": "http://www.deri.ie/",
  "icon": "http://www.deri.ie/icon.jpg",
  "label": {"en-GB": "Screen - DERI"},
  "postconditions": [],
  "preconditions": ["?person rdf:type foaf:Person . 
                     ?person foaf:workplaceHomepage http://www.deri.ie/"],
  "rights": "http://creativecommons.org/",
  "screenshot": "http://www.deri.ie/screenshot.jpg",
  "uri": "http://www.morfeoproject.eu/fast/fco#Screen1234552194269",
  "version": "1.0"
}
\end{verbatim}

To obtain all the screens stored in the catalogue a HTTP GET request is sent to the Collection URI and the response may be something like this:
\begin{verbatim}
[
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "http://www.ismaelrivera.es/",
    "description": {"en-gb": "Returns people working in DERI"},
    "domainContext": {
      "tags": [],
      "user": null
    },
    "homepage": "http://www.deri.ie/",
    "icon": "http://www.deri.ie/icon.jpg",
    "label": {"en-gb": "Screen - DERI"},
    "postconditions": ["?person rdf:type foaf:Person . 
                        ?person foaf:workplaceHomepage http://www.deri.ie/"],
    "preconditions": [],
    "rights": "http://creativecommons.org/",
    "screenshot": "http://www.deri.ie/screenshot.jpg",
    "uri": "http://www.morfeoproject.eu/fast/fco#Screen1234552164472",
    "version": "1.0"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "http://www.ismaelrivera.es/",
    "description": {"en-gb": "Show information about a person working in DERI"},
    "domainContext": {
      "tags": [],
      "user": null
    },
    "homepage": "http://www.deri.ie/",
    "icon": "http://www.deri.ie/icon.jpg",
    "label": {"en-gb": "Screen - DERI"},
    "postconditions": [],
    "preconditions": ["?person rdf:type foaf:Person . 
                       ?person foaf:workplaceHomepage http://www.deri.ie/"],
    "rights": "http://creativecommons.org/",
    "screenshot": "http://www.deri.ie/screenshot.jpg",
    "uri": "http://www.morfeoproject.eu/fast/fco#Screen1234552194269",
    "version": "1.0"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "http://www.ismaelrivera.es/",
    "description": {"en-gb": "Show information about a person"},
    "domainContext": {
      "tags": [],
      "user": null
    },
    "homepage": "http://www.deri.ie/",
    "icon": "http://www.deri.ie/icon.jpg",
    "label": {"en-gb": "Screen - DERI"},
    "postconditions": [],
    "preconditions": ["?person rdf:type foaf:Person"],
    "rights": "http://creativecommons.org/",
    "screenshot": "http://www.deri.ie/screenshot.jpg",
    "uri": "http://www.morfeoproject.eu/fast/fco#Screen1234552373865",
    "version": "1.0"
  }
]
\end{verbatim}

\subsubsection{CRUD operations for Screen-Flows} % (fold)

A screenflow is a resource which can be created, retrieved, modified or deleted since the catalogue provides CRUD support for screenflows. These features are provided following the REST philosophy, using the HTTP methods. As in the previous section the concepts \emph{collection} and \emph{member} are used including their URLs. Table \ref{tab:crud_screenflows} details the operations offered for screen-flows.

\begin{table}[htb]
\caption{CRUD operations for Screen-Flows}
\label{tab:crud_screenflows}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{2.5cm}|p{3.5cm}|p{5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Resource} &
                         \textcolor{white}{HTTP method} &
                         \textcolor{white}{HTTP body} &
                         \textcolor{white}{Description}\\ \hline
Collection URI & GET & N/A & \textbf{List} the members of the collection.\\ \hline
Collection URI & PUT & N/A & Not used.\\ \hline
Collection URI & POST & JSON representation of the screen-flow & \textbf{Create} a new entry in the collection where the URI is assigned automatically by the collection. The URI created is returned by this operation.\\ \hline
Collection URI & DELETE & N/A & Not used.\\ \hline
Member URI & GET & N/A & \textbf{Retrieve} the addressed member of the collection.\\ \hline
Member URI & PUT & JSON representation of the screen-flow & \textbf{Update} the addressed member of the collection or create it with a defined URI.\\ \hline
Member URI & POST & N/A & Not used. \\ \hline
Member URI & DELETE & N/A & \textbf{Delete} the addressed member of the collection.\\ \hline
\end{tabular}
\end{center}
\end{table}

The following is an example of the request and response while creating a screen-flow:
\begin{verbatim}
{
  "uri": null,
  "label": {"en-GB": "My First ScreenFlow"},
  "description": {"en-GB": "A example of screenflow"},
  "creationDate": "2009-02-05T13:11:41+0000",
  "creator": "http://www.ismaelrivera.es/",
  "domainContext": {
    "tags": ["people"],
    "user": null
  },
  "homepage": "http://www.screenflow.com/",
  "icon": "http://www.screenflow.com/icon.jpg",
  "screenshot": "http://www.screenflow.com/screenshot.jpg",
  "rights": "http://creativecommons.org/",
  "version": "1.0",
  "preconditions": [],
  "postconditions": [],
  "screens": [
    "http://www.morfeoproject.eu/fast/fco#Screen1233750841383",
    "http://www.morfeoproject.eu/fast/fco#Screen1233750828836",
    "http://www.morfeoproject.eu/fast/fco#Screen1233750820914"
  ]
}
\end{verbatim}

\begin{verbatim}
{
  "creationDate": "2009-02-05T13:11:41+0000",
  "creator": "http://www.ismaelrivera.es/",
  "description": {"en-GB": "A example of screenflow"},
  "domainContext": {
    "tags": ["people"],
    "user": null
  },
  "homepage": "http://www.screenflow.com/",
  "icon": "http://www.screenflow.com/icon.jpg",
  "label": {"en-GB": "My First ScreenFlow"},
  "postconditions": [],
  "preconditions": [],
  "rights": "http://creativecommons.org/",
  "screens": [
    "http://www.morfeoproject.eu/fast/fco#Screen1233750841383",
    "http://www.morfeoproject.eu/fast/fco#Screen1233750828836",
    "http://www.morfeoproject.eu/fast/fco#Screen1233750820914"
  ],
  "screenshot": "http://www.screenflow.com/screenshot.jpg",
  "uri": "http://www.morfeoproject.eu/fast/fco#ScreenFlow1233752391898",
  "version": "1.0"
}
\end{verbatim}

\subsubsection{Find} % (fold)

The find operation search inside the catalogue for any screen which could be somehow related to the gadget the user is creating. It provides a recommended set of screens depending on the domain context, the canvas, etc. The specific URL to access this operation is http://catalogueURL/find using HTTP POST method. From now on, the method 'find' only considers the domain context, being a list of tags and the pre/postconditions of the screens. It will try to satisfy all the unsatisfied preconditions of a given list of screens also known as canvas. The results will be all the screens stored in the catalogue which fulfil some of these preconditions, and are tagged with the tags specified in the domain context. The request parameters are shown in Table \ref{tab:find_request} and the response parameters are shown in Table \ref{tab:find_response}.

\begin{table}[htb]
\caption{Find Request Parameters}
\label{tab:find_request}
\begin{center}
\begin{tabular}{|p{2cm}|p{9.5cm}|p{2cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Name} &
                         \textcolor{white}{Description} &
                         \textcolor{white}{Type}\\ \hline
Canvas & The canvas is composed by a list of screens. Only the URI is needed. & Optional \\ \hline
Domain Context & The domain context contains a list of tags and a user. & Optional \\ \hline
Elements & It is a list of resources, previously stored in the catalogue. For example, the list of screens recommended last execution. Only accepts screens. & Optional \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[htb]
\caption{Find Response Parameters}
\label{tab:find_response}
\begin{center}
\begin{tabular}{|p{2cm}|p{9.5cm}|p{2cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Name} &
                         \textcolor{white}{Description} &
                         \textcolor{white}{Type}\\ \hline
N/A & A list of recommended screens is returned. & Required \\ \hline
\end{tabular}
\end{center}
\end{table}

Following is shown an example of usage of this operation considering a canvas with the screen \texttt{http://www.morfeoproject.eu/fast/fco\#Screen1234552373865}.

\begin{verbatim}
{
  canvas: [
    {
      uri: "http://www.morfeoproject.eu/fast/fco#Screen1234552373865"
    }
  ],
  domainContext: {
    tags: [],
	  user: null
  },
  elements: []
}
\end{verbatim}

@@

\begin{verbatim}
[{
  "creationDate": "2009-02-07T09:59:52+0000",
  "creator": "http://www.ismaelrivera.es/",
  "description": {"en-gb": "Returns people working in DERI"},
  "domainContext": {
    "tags": [],
    "user": null
  },
  "homepage": "http://www.deri.ie/",
  "icon": "http://www.deri.ie/icon.jpg",
  "label": {"en-gb": "Screen - DERI"},
  "postconditions": ["?person rdf:type foaf:Person . 
                      ?person foaf:workplaceHomepage http://www.deri.ie/"],
  "preconditions": [],
  "rights": "http://creativecommons.org/",
  "screenshot": "http://www.deri.ie/screenshot.jpg",
  "uri": "http://www.morfeoproject.eu/fast/fco#Screen1234552164472",
  "version": "1.0"
}]
\end{verbatim}

\subsubsection{Check} % (fold)

This operation verifies the state of certain list of screens depending on a specific criterion. The only criterion accepted in this stage of the prototype is 'reachability'. A screen will be reachable if it all its preconditions are satisfied by postconditions of the screens the canvas contain. The specific URL to access this operation is http://catalogueURL/check using HTTP POST method.

\begin{table}[htb]
\caption{Check Request Parameters}
\label{tab:check_request}
\begin{center}
\begin{tabular}{|p{2cm}|p{9.5cm}|p{2cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Name} &
                         \textcolor{white}{Description} &
                         \textcolor{white}{Type}\\ \hline
Canvas & The canvas is composed by a list of screens. Only the URI is needed. & Optional\\ \hline
Domain Context & The domain context contains a list of tags and a user. & Optional\\ \hline
Elements & It is a list of resources, previously stored in the catalogue. For example, the list of screens recommended last execution. Only accepts screens. & Optional\\ \hline
Criterion & The criterion specifies what it has to be check. The only possible supported now is 'reachability' in order to check if the preconditions of a screen are satisfied. & Required\\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[htb]
\caption{Check Response Parameters}
\label{tab:check_response}
\begin{center}
\begin{tabular}{|p{2cm}|p{9.5cm}|p{2cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Name} &
                         \textcolor{white}{Description} &
                         \textcolor{white}{Type}\\ \hline
Canvas & The canvas indicating which screens satisfy the critetion. More aditional information may be included, for example, a satisfaction attribute for every precondition for reachability. & Optional\\ \hline
Domain Context & The domain context contains a list of tags and a user. & Optional\\ \hline
Elements & The elements indicating which satisfy the critetion. More aditional information may be included as in the Canvas. & Optional\\ \hline
\end{tabular}
\end{center}
\end{table}

The scenario for the following example is composed by a screen in the canvas which precondition is a foaf:Person which foaf:workplaceHomepage is http://www.deri.ie/, and a screen in the elements list which precondition is a foaf:Person. The state to check in this case is the reachability and satisfaction of the screens and preconditions.

\begin{verbatim}
{
  canvas: [
    {
      uri: "http://www.morfeoproject.eu/fast/fco#Screen1234552194269"
    }
  ],
  domainContext: [],
  elements: [
    {
      uri: "http://www.morfeoproject.eu/fast/fco#Screen1234552373865"
    }  
  ],
  criterion: "reachability"
}
\end{verbatim}

As you can see in the response, no screen is reachable at the moment, and no precondition is satisfied.

>>>>

\subsection{Changes from previous version} % (fold)
\label{sub:changes_from_previous_version}

@@

\begin{itemize}
	\item Section \ref{sec:installation_guide}. Installation Guide describes a set of steps to be followed in order to install and execute the FAST Catalogue. Also some configuration instructions are specified.
	\item Section \ref{sub:content_negotiation}. Content Negotiation states how the FAST Catalogue has adopted several of the content negotiation principles.
	\item Section \ref{sec:restful_catalogue_api}. RESTful Catalogue API has been intensively extended and modified in order to  reflect all the new functionality and how every request or response is constructed. Some of the most important features added in this iteration are:
	\begin{itemize}
		\item support for form elements, operators and back-end services (see Section ...),
		\item convenience operations for recommendation and checking satisfaction and reachability for form elements, operators and back-end services (see Section ...),
		\item and, last but not least, support for Screen planning (see Section \ref{sub:planning}).
	\end{itemize}
	\item Several appendixes have been added with the JSON structure of every building block the Catalogue can deal with.
\end{itemize}

% subsection changes_from_previous_version (end)

@@

The format supported, and in which they must be constructed, by every HTTP request is JSON\footnote{http://www.json.org/}. JSON is a lightweight data interchange format whose simplicity has resulted in widespread use among web developers, easy to read and write and able to using any programming language because its structures map directly to data structures used in most programming languages.

Every HTTP request should be encoded using the MIME type \texttt{application/json} and the charset \texttt{UTF-8}.

The following is an example of a Find \& Check request:

\begin{verbatim}
{
  "canvas": [
    { "uri": "http://localhost:8080/catalogue/screens/238" },
    { "uri": "http://localhost:8080/catalogue/screens/323" }
  ],
  "elements": [
    { "uri": "http://localhost:8080/catalogue/screens/636" }
  ],
  "domainContext": {
    "tags": [
      {
        "label": { "en-GB": "Amazon" },
        "means": "http://dbpedia.org/page/Amazon.com"
      }
    ],
    "user": "irivera",
  },
  "criterion": "reachability"
}
\end{verbatim}

@@

In order to offers an adaptable solution to various languages and regions without major engineering changes, internationalisation is considered from an early stage in the catalogue development. Underlying representation technologies used to develop the catalogue (RDF/XML and JSON) allow to implement this feature. This feature is implemented by the addition of a language tag to every 'string' desired. The specification of this language tag is composed by the language code and the country code, following the ISO 639\footnote{http://ftp.ics.uci.edu/pub/ietf/http/related/iso639.txt} for languages and the ISO 3166\footnote{http://userpage.chemie.fu-berlin.de/diverse/doc/ISO\_3166.html} for countries. The following example illustrates how to use it properly in both formats.

@@

Until now, using internationalisation is allowed for the label and the description of a screen, but in the near future, more attributes will benefit from this feature.

@@

\subsubsection{CRUD operations} % (fold)

Any building block within the Catalogue is a resource in terms of REST philosophy, hence it can be created, retrieved, modified or deleted, using a certaing URL and a specific HTTP method for every operation. Two concepts have to be defined: \emph{collection}, as a set of resources which access URI is http://catalogueURL/<type>/ where catalogueURL is the specific URL where the Catalogue server is installed and <type> is the plural of the name of the building block (e.g. screens, services), and \emph{member} of the collection, in other words, the building block itself, which access URI is http://catalogueURL/<type>/<id> where the <id> has to be replaced by the identifier of a specific building block. The details of the operations and which HTTP verb has to be used can be found in the Table \ref{tab:crud_operations}.

\begin{table}[htb]
\caption{CRUD operations}
\label{tab:crud_operations}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{2.5cm}|p{3.5cm}|p{5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Resource} &
                         \textcolor{white}{HTTP method} &
                         \textcolor{white}{HTTP body} &
                         \textcolor{white}{Description}\\ \hline
Collection URI & GET & N/A & \textbf{List} the members of the collection.\\ \hline
Collection URI & PUT & N/A & Not used.\\ \hline
Collection URI & POST & JSON representation of the building block & \textbf{Create} a new entry in the collection where the URI is assigned automatically by the collection. The URI created is returned by this operation.\\ \hline
Collection URI & DELETE & N/A & Not used.\\ \hline
Member URI & GET & N/A & \textbf{Retrieve} the addressed member of the collection.\\ \hline
Member URI & PUT & JSON representation of the building block & \textbf{Update} the addressed member of the collection or create it with a defined URI.\\ \hline
Member URI & POST & N/A & Not used. \\ \hline
Member URI & DELETE & N/A & \textbf{Delete} the addressed member of the collection.\\ \hline
\end{tabular}
\end{center}
\end{table}

The JSON structure for create any building bock can be found in the appendixes. All of them are composed of a common structure which can be found in Section \ref{appendix_b}, and some specific information depending on the type. Screen-flows are defined in \ref{appendix_c}, screens in \ref{appendix_d} and forms, operators and back-end services share the same structure detailed in \ref{appendix_e}. However, a few examples of request and responses are shown in order to clarify how the request are constructed and sent, and how the responses look like.

To create a new screen, a POST request is send to the catalogue server, including the JSON representation of the screen as the body of the request:

\begin{verbatim}
{
  "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
  "creationDate": "2010-01-26T17:01:13+0000",
  "creator": "irivera",
  "description": {"en-gb": "Please fill the description..."},
  "homepage": "http://fast.morfeo-project.eu/",
  "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
  "id": "28",
  "label": {"en-gb": "Amazon Product List"},
  "name": "ProductList",
  "postconditions": [
    [
      {
        "id": "item",
        "label": { "en-gb": "An item" },
        "pattern": "?I 
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#Item",
        "positive": "true"
      }
    ]
  ],
  "preconditions": [
    [
      {
        "id": "filter",
        "label": { "en-gb": "A search criteria" },
        "pattern": "?F
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#SearchCriteria",
        "positive": "true"
      }
    ]
  ],
  "rights": "http://creativecommons.org/",
  "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
  "tags": [{"label": {"en-gb": "amazon"}}],
  "version": "0.1"
}
\end{verbatim}

The URI of the screen is created using the id specified in the JSON request. So, the response for this operation is:

\begin{verbatim}
{
  "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
  "creationDate": "2010-01-26T17:01:13+0000",
  "creator": "irivera",
  "description": {"en-gb": "Please fill the description..."},
  "homepage": "http://fast.morfeo-project.eu/",
  "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
  "id": "28",
  "label": {"en-gb": "Prueba1"},
  "name": "ProductList",
  "postconditions": [
    [
      {
        "id": "item",
        "label": { "en-gb": "An item" },
        "pattern": "?I
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#Item",
        "positive": "true"
      }
    ]
  ],
  "preconditions": [
    [
      {
        "id": "filter",
        "label": { "en-gb": "A search criteria" },
        "pattern": "?F
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#SearchCriteria",
        "positive": "true"
      }
    ]
  ],
  "rights": "http://creativecommons.org/",
  "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
  "tags": [{"label": {"en-gb": "amazon"}}],
  "type": "screen",
  "uri": "http://localhost:8080/catalogue/screens/28",
  "version": "0.1"
}
\end{verbatim}

To obtain all the screens stored in the catalogue a HTTP GET request is sent to the Collection URI and the response may be something like this:
\begin{verbatim}
[
  {
    "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
    "creationDate": "2010-01-26T17:01:13+0000",
    "creator": "irivera",
    "description": {"en-gb": "Please fill the description..."},
    "homepage": "http://fast.morfeo-project.eu/",
    "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
    "id": "28",
    "label": {"en-gb": "Prueba1"},
    "name": "ProductList",
    "postconditions": [
      [
        {
          "id": "item",
          "label": { "en-gb": "An item" },
          "pattern": "?I
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#Item",
          "positive": "true"
        }
      ]
    ],
    "preconditions": [
      [
        {
          "id": "filter",
          "label": { "en-gb": "A search criteria" },
          "pattern": "?F
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#SearchCriteria",
          "positive": "true"
        }
      ]
    ],
    "rights": "http://creativecommons.org/",
    "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
    "tags": [{"label": {"en-gb": "amazon"}}],
    "type": "screen",
    "uri": "http://localhost:8080/catalogue/screens/28",
    "version": "0.1"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "fabio",
    ...,
	  "uri": "http://localhost:8080/catalogue/screens/14",
    "version": "1.0"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "javier",
    ...,
	  "uri": "http://localhost:8080/catalogue/screens/564",
    "version": "1.0"
  }
]
\end{verbatim}

\subsubsection{Screen Find} % (fold)
\label{ssub:screen_find}

The find operation searches inside the catalogue for any screen which could be somehow related to the gadget the user is creating. It provides a recommended set of screens depending on the domain context, the canvas, and so on.

The specific URL to access this operation is http://catalogueURL/screens/find using HTTP POST method. From now on, the method 'find' only considers the domain context and the pre/postconditions of the screens. It will try to satisfy all the unsatisfied preconditions of a given list of screens also known as canvas. The results will be all the screens stored in the catalogue which fulfil some of these preconditions, and are tagged with the tags specified in the domain context. The request parameters are shown in Table \ref{tab:screen_find_request} and the response parameters are shown in Table \ref{tab:screen_find_response}.

\begin{table}[htb]
\caption{Screen Find Request Parameters}
\label{tab:screen_find_request}
\begin{center}
\begin{tabular}{|p{2cm}|p{9.5cm}|p{2cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Name} &
                         \textcolor{white}{Description} &
                         \textcolor{white}{Type}\\ \hline
canvas & The canvas is composed by a list of screens. Only the URI is needed. & Optional \\ \hline
domainContext & The domain context contains a list of tags and a user. & Optional \\ \hline
elements & It is a list of resources, previously stored in the catalogue. For example, the list of screens recommended last execution. Only accepts screens. & Optional \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[htb]
\caption{Screen Find Response Parameters}
\label{tab:screen_find_response}
\begin{center}
\begin{tabular}{|p{2cm}|p{9.5cm}|p{2cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Name} &
                         \textcolor{white}{Description} &
                         \textcolor{white}{Type}\\ \hline
N/A & A list of recommended screens URIs is returned. & Required \\ \hline
\end{tabular}
\end{center}
\end{table}

Following is shown an example of usage of this operation considering a canvas with the screen \texttt{http://localhost:8080/catalogue/screens/654}.

\begin{verbatim}
{
  canvas: [
    { uri: "http://localhost:8080/catalogue/screens/654" }
  ],
  domainContext: {
    tags: [],
	  user: null
  },
  elements: []
}
\end{verbatim}

@@

\begin{verbatim}
[
  "http://localhost:8080/catalogue/screens/371",
  "http://localhost:8080/catalogue/screens/24",
  "http://localhost:8080/catalogue/screens/253",
  "http://localhost:8080/catalogue/screens/12"
]
\end{verbatim}

\subsubsection{Screen Check} % (fold)
\label{ssub:screen_check}

This operation verifies the state of certain list of screens depending on a specific criterion. The only criterion accepted in this stage of the prototype is 'reachability'. A screen will be reachable if it all its preconditions are satisfied by postconditions of the screens the canvas contain. The specific URL to access this operation is http://catalogueURL/screens/check using HTTP POST method.

\begin{table}[htb]
\caption{Screen Check Request Parameters}
\label{tab:screen_check_request}
\begin{center}
\begin{tabular}{|p{2cm}|p{9.5cm}|p{2cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Name} &
                         \textcolor{white}{Description} &
                         \textcolor{white}{Type}\\ \hline
canvas & The canvas is composed by a list of screens. Only the URI is needed. & Optional\\ \hline
domainContext & The domain context contains a list of tags and a user. & Optional\\ \hline
elements & It is a list of resources, previously stored in the catalogue. For example, the list of screens recommended last execution. Only accepts screens. & Optional\\ \hline
criterion & The criterion specifies what it has to be check. The only possible supported now is 'reachability' in order to check if the preconditions of a screen are satisfied. & Required\\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[htb]
\caption{Screen Check Response Parameters}
\label{tab:screen_check_response}
\begin{center}
\begin{tabular}{|p{2cm}|p{9.5cm}|p{2cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Name} &
                         \textcolor{white}{Description} &
                         \textcolor{white}{Type}\\ \hline
Canvas & The canvas indicating which screens satisfy the critetion. More aditional information may be included, for example, a satisfaction attribute for every precondition for reachability. & Optional\\ \hline
Domain Context & The domain context contains a list of tags and a user. & Optional\\ \hline
Elements & The elements indicating which satisfy the critetion. More aditional information may be included as in the Canvas. & Optional\\ \hline
\end{tabular}
\end{center}
\end{table}

The scenario for the following example is composed by a screen in the canvas which precondition is a foaf:Person which foaf:workplaceHomepage is \url{http://www.deri.ie/}, and a screen in the elements list which precondition is a foaf:Person. The state to check in this case is the reachability and satisfaction of the screens and preconditions.

\begin{verbatim}
{
  "canvas": [
    { "uri": "http://localhost:8080/catalogue/screens/238" }
  ],
  "elements": [
    { "uri": "http://localhost:8080/catalogue/screens/636" }
  ],
  "domainContext": {
    "tags": [
      {
        "label": { "en-GB": "Amazon" },
        "means": "http://dbpedia.org/page/Amazon.com"
      }
    ],
    "user": "irivera",
  },
  criterion: "reachability"
}
\end{verbatim}

The response shows that there are not reachable screens at the moment, and preconditions are not satisfied.

\begin{verbatim}
{
  "canvas": [{
    "preconditions": [{
      "label": {"en-gb": "A person working in DERI"},
      "pattern": "?person rdf:type foaf:Person . 
                  ?person foaf:workplaceHomepage http://www.deri.ie/",
      "positive": true,
      "satisfied": false
    }],
    "reachability": false,
    "uri": "http://localhost:8080/catalogue/screens/238"
  }],
  "elements": [{
    "preconditions": [{
      "label": {"en-gb": "A person"},
      "pattern": "?person rdf:type foaf:Person",
      "satisfied": false
    }],
    "reachability": false,
    "uri": "http://localhost:8080/catalogue/screens/636"
  }]
}
\end{verbatim}

\subsubsection{Screen Find \& Check} % (fold)
\label{ssub:screen_findcheck}

For convenience and to minimise the number of request, the Find operation may be combined with the Check operation. This operation will look for new screens based on the given information, and will perform the Check to both the screens in the canvas and the screens in the \emph{elements} attribute.

The format of the request is the same as the one used in the Check operation:
